It Is Unbearable To Breath Here': Air Quality, Open Incineration, And Misinformation In Blantyre, Malawi

### 2023-04-06 manuscript/manuscript.qmd
Add reproducibility and data statement

bibliography: man-qechairquality.bib

@@

@@

@@

dat_in_ratios <- dat_in |> 
  mutate(date = as_date(date_time)) |> 
  mutate(hour = hour(date_time)) |> 
  group_by(date, hour, location, indicator) |> 
  summarise(mean = mean(value)) |> 
  pivot_wider(names_from = indicator, 
              values_from = mean) |> 
  mutate(p10_pm25_ratio = pm10/pm25)  |>

>>>>

bibliography: [man-qechairquality.bib, packages.bib]

@@

knitr::write_bib(file = here::here("manuscript/packages.bib"))

@@

### Computational reproducibility and data availability

R Statistical Software version 4.2.1, RStudio IDE version 2023.3.0.386, and Quarto scientific publishing system version were used for quantitative data analysis and writing of the manuscript [@R-base; @allaire2022quartoa; @positteam2023rstudio]. A set of additional R packages were used for data wrangling, analysis, and visualisation [@ggplot22016; @lubridate2011;  @R-dplyr; @R-forcats; @R-ggplot2; @R-janitor; @R-leaflet; @R-lubridate; @R-mapview; @R-readr; @R-tidyr; @R-waffle].

Raw data and analysis-ready processed data is available as an R package at @R-qechairquality. The data underlying the tables and figures of this manuscript are contained in a repository alongside a reproducible document that contains the analysis code and the written narrative of the manuscript [TODO: manuscript software citation].

@@

dat_in_ratios <- dat_in |> 
  mutate(date = as_date(date_time)) |> 
  mutate(hour = hour(date_time)) |> 
  group_by(date, hour, location, indicator) |> 
  summarise(mean = mean(value)) |> 
  pivot_wider(names_from = indicator, 
              values_from = mean) |> 
  mutate(p10_pm25_ratio = pm10/pm2.5)  |>
